---
title: "DATA608 HW2"
author: "Bin Lin"
date: "2017-9-23"
output: html_document
---

```{r, comment=NA}
#install.packages("devtools")

devtools::install_github("hadley/bigvis")

suppressWarnings(library(ggplot2))
suppressWarnings(library(dplyr))
suppressWarnings(library(bigvis))
```

1. After a few building collapses, the City of New York is going to begin investigating older
buildings for safety. However, the city has a limited number of inspectors, and wants to find a
'cut-off' date before most city buildings were constructed. Build a graph to help the city
determine when most buildings were constructed. Is there anything in the results that causes
you to question the accuracy of the data? (note: only look at buildings built since 1850)


I think the data is zero inflated because there are more than 44000 data entries have the YearBuilt of zero. This really affects the validity of the data, since when I try to create graphs, I would have to eliminate those data entries. 

```{r}
BK <- read.csv("BORO_zip_files_csv/BK.csv")
BX <- read.csv("BORO_zip_files_csv/BX.csv")
MN <- read.csv("BORO_zip_files_csv/MN.csv")
QN <- read.csv("BORO_zip_files_csv/QN.csv")
SI <- read.csv("BORO_zip_files_csv/SI.csv")

all_PLUTO_data <- rbind(BK, BX, MN, QN, SI)
sub1 <- all_PLUTO_data %>%
  filter(YearBuilt >= 1850 & YearBuilt <= 2017)

#The boxplot shows around 50% of houses were built between 1920 and 1960s with a peak around 1920 to 1930, according to the range of first quantile.   
boxplot(sub1$YearBuilt)
quantile(sub1$YearBuilt, 0.25)
quantile(sub1$YearBuilt, 0.5)



#The condensed data based on count shows a peak around 1920 and 1930 which is pretty much the same as what is shown in the boxplot.
a <- condense(bin(sub1$YearBuilt, 5))
autoplot(a) + labs(x = "Years Built", y = "Number of Buildings")
ggsave("Figure1.jpg")
```


2. The city is particularly worried about buildings that were unusually tall when they were
built, since best-practices for safety hadn't yet been determined. Create a graph that shows
how many buildings of a certain number of floors were built in each year (note: you may
want to use a log scale for the number of buildings). It should be clear when 20-story
buildings, 30-story buildings, and 40-story buildings were first built in large numbers.

```{r}
sub2<- sub1%>%
  filter(NumFloors >= 20, NumFloors <= 40)%>%
  select(YearBuilt, NumFloors)


#The condensed data showed most tall buildings were built during 1960s. During 1930s, there is a peak but it quickly faded and after 2000, US again start build tall buildings.

b <- condense(bin(sub2$NumFloors, 10), bin(sub2$YearBuilt, 5))
autoplot(b) + labs(x = "Building Stories", y = "Years Built")
ggsave("Figure2.jpg")
```


3. Your boss suspects that buildings constructed during the US's involvement in World War
II (1941-1945) are more poorly constructed than those before and after the way due to the
high cost of materials during those years. She thinks that, if you calculate assessed value
per floor, you will see lower values for buildings at that time vs before or after. Construct a
chart/graph to see if she's right.

```{r}
sub3 <- all_PLUTO_data %>%
  filter(NumFloors > 0, AssessLand > 0, AssessTot > 0, YearBuilt > 1920, YearBuilt < 1960)%>%
  select(YearBuilt, NumFloors, AssessLand, AssessTot)%>%
  group_by(YearBuilt)%>%
  mutate(AssessValuePerFloor = (sum(AssessTot) - sum(AssessLand)) / sum(NumFloors))

#The following line chart clearly shows during WWII, the assess value per floor is relatively low compare to those houses that were built later. However, if we compare the value against those that were built before WWII, the differences were not that obvious. This tells us that the war is probably not the reason why we have lower assessed value per floor for those buildings, but The Great Depression was the main reason, because The Great Depression lasted longer compare to the wartime.  

ggplot() + geom_line(data = sub3, aes(x = YearBuilt, y = AssessValuePerFloor)) + labs(x = "Year Built", y = "Assessed Value Per Floor")

ggsave("Figure3.jpg")
```